Reconstruction of Charge Number of Heavy Cosmic Rays using Cherenkov Light

### 2016-04-27 report/draft1.tex
Backup 27/4/16

From the subset of pixels satisfying these conditions, the DC pixel was selected as the remaining pixel with $Q_{DC}$. The result was compared with the true DC pixel, identified from the hadron-only image, to test the accuracy of this cut. Out of 400 events, it was fount that only 55\% of these events contained a clear DC signal, as defined by requiring the DC pixel to have $Count_{DC} > 5500$ in the hadron-only image. SOMETHING! Of this subset of 'DC events', 17\% events passed all of the required cuts. The QDC was found to be 100\% accurate in identifying the DC pixel in those passing events.

@@

With this cut applied, out of 1896 events, it was fount that only 55\% of these events contained a clear DC signal, as defined by requiring the DC pixel to have $Count_{DC} > 5500$ in the hadron-only image. Of this subset of 'DC events', 46\% events passed all of the required cuts. The BDT was found to be 75 \% accurate in identifying the DC pixel in those passing events.

In FIG, a plot of true vs. reconstructed DC count is shown, obtained by comparing the BDT selected pixel to the hadron-only DC pixel. The black line indicates the optimal 1:1 ratio that we are aiming for. It is seen that there the vast majority of misidentified events have a small $candidate_{DC count}$, forming a red line in the region $candidate_{DC count} \approx 0$. To remove these misidentified events, we can apply a second cut requiring $candidate_{DC count} > 300$.

Application of this combined cut greatly increases the successful identification rate. Of the 2000 events, 84\% of events passed all of the required cuts. The BDT was found to be 90 \% accurate in identifying the DC pixel in those passing events. This represents a very significant improvement in DC pixel identification over the previous QDC method, and corresponds to a fivefold increase in the number of HESS data events that can be studied using the LPD method.

\subsection{Error in calculated $Count_{DC}$}
Having successfully identified the DC pixel in many events, we can calculate the difference between the derived $candidate_{DC count}$ and the hadron-only $True_{DC}$ to determine the error we will find for the LPD. Binning the difference $\Delta = candidate_{DC count} - True_{DC count}$ as shown in FIG, we find that the mean difference is 65 and the median difference is -75. We thus see that the distribution is not significantly skewed. However, the Standard deviation is approximately 600 when measured both by half of the difference from the 16th to 84th centile, and by 68th centile of an absolute difference. This again suggests that, although skewed, the fraction error in intensity is rather large.

@@

@@

\subsection{Energy Considerations}
Cosmic Rays follow a well-defined power law where $ \frac{dN(E)}{dt} \propto E^{-\gamma} $ and experimentally $ \gamma = 2.7 \pm ? $. Consequently higher energy Cosmic Rays are heavily suppressed. The Energy Threshold for Cherenkov Light Emission as a function of height is illustrated in \ref{fig:generalenergy}. Once the Energy of a Cosmic Ray exceeds the local Cherenkov Energy Threshold of the atmosphere, the Nucleus will begin emitting a ring of Cherenkov Light. Emission continues until the first interaction with the atmosphere, occurring at a randomly distributed height we call $h$. Then for a given Telescope Array altitude above sea level, simple trigonometry yields the radius of the LDF on the ground:
\[ Radius(height = altitude_{array}) = \tan [\theta_{C}(h)] \times (h - altitude_{array})\]

The Refractive Index of the atmosphere, and thus the Cherenkov angle $\theta_{C}$, increases as the altitude decreases. Thus the upper atmosphere emission contributes to the inner LDF, while the lower atmosphere emission contributes to the outer LDF. We can also see ground emission radius as a function of height in \ref{fig:generalenergy}. We find that the high-radius emission (occurring near the first interaction region) varies little between different high energies. We deem this to be \textquoteleft Saturated Emission\textquoteright.

\subsection{Nuclear Charge}
Cherenkov Emission is determined by the Frank Tamm formula!!!!!

Under the assumption of constant magnetic permittivity and a zenith angle of $90\degree$ we can use the approximate form \[ N_{photons} \approx (37000 \times Z^{2} \times \Delta_{h} \times \Delta_{E})\] where $\Delta_{h}$ is the vertical distance travelled in meters and $\Delta_{E}$ is the emission energy range in eV.

\subsection{Energy saturation region}
However, in the 4 telescope height region, the Cherenkov Threshold Energy is $ E_{Threshold} \approx 0.35$ TeV per Nucleon as shown in \ref{fig:lpd}! The saturation in for these heights occurs roughly at 0.7 TeV per Nucleon or something...

NOW I KNOW!

>>>>

From the subset of pixels satisfying these conditions, the remaining pixel with the largest $Q_{DC}$ was selected as the DC pixel. The result was compared with the true DC pixel, identified from the hadron-only image, to test the accuracy of this cut. Out of 400 events, it was fount that only 55\% of these events contained a clear DC signal, as defined by requiring the DC pixel to have $Count_{DC} > 5500$ in the hadron-only image. SOMETHING! Of this subset of 'DC events', 17\% events passed all of the required cuts. The QDC was found to be 100\% accurate in identifying the DC pixel in those passing events \ref{fig:cutdistribution}.

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{cutdistribution}
\caption{The DC signal in the shower-free pixel is shown in the top left, with a broad gaussian distribution with the tail of the night-sky background extending up to appproximately 5000. Events below this are unlikely to be identified correctly because the DEC light is too faint. In the top right- the distribution of the dataset is shown, once all the non-QDC cuts have been applied. In the bottom left, the BDT score distribution is shown before any cuts. On the bottom right, we see the same distribution after both signal and BDT score cuts are applied. All green events are ones in which the DC pixel has been correctly identified, while red events are ones that have been incorrectly identified.}
\label{fig:cutdistribution}
\end{center}
\end{figure}

@@

With this cut applied, out of 1200 events, 46\% events passed all of the required cuts. The BDT was found to be 75 \% accurate in identifying the DC pixel in those passing events.

In \ref{fig:cutdistribution}, a plot of true vs. reconstructed DC count is shown, obtained by comparing the BDT selected pixel to the hadron-only DC pixel. The black line indicates the optimal 1:1 ratio that we are aiming for. It is seen that there the vast majority of misidentified events have a small $candidate_{DC count}$, forming a red line in the region $candidate_{DC count} \approx 0$. To remove these misidentified events, we can apply a second cut requiring $candidate_{DC count} > 300$.

Application of this combined cut greatly increases the successful identification rate. Of the 2000 events, 84\% of events passed all of the required cuts. The BDT was found to be 90 \% accurate in identifying the DC pixel in those passing events. This represents a very significant improvement in DC pixel identification over the previous QDC method, and corresponds to a fivefold increase in the number of HESS data events that can be studied using the LPD method. Use of this BDT method is thus assumed throughout the rest of this analysis.

\subsection{Error in calculated $Count_{DC}$}
Having successfully identified the DC pixel in many events, we can calculate the difference between the derived $candidate_{DC count}$ and the hadron-only $True_{DC}$ to determine the error we will find for the LPD. Binning the difference $\Delta = candidate_{DC count} - True_{DC count}$ as shown in FIG, we find that the mean difference is 65 and the median difference is -75. We thus see that the distribution is not significantly skewed. However, the Standard deviation is approximately 600 when measured both by half of the difference from the 16th to 84th centile, and by 68th centile of an absolute difference. This again suggests that, although skewed, the fraction error in intensity is rather large. However, the fractional error found purely on the basis of QDC calculations is EQUALLY LARGE??LARGER?.

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{DCcounterror}
\caption{The difference between true and reconstructed DC signal for events passing the cuts is shown in the top left. In the top right the same is shown for events which were rejected. The true DC signals for events which passed the cuts is plotted against the reconstructed signals in the lower left, and for rejected events in the lower right. As in \ref{fig:cutdistribution}, in all plots a green event is one in which the DC pixel has been correctly identified, while a red event is one that has been incorrectly identified.}
\label{fig:dcdiff}
\end{center}
\end{figure}

@@

\subsection{Cherenkov Emission}
Cosmic Rays follow a well-defined power law where $ \frac{dN(E)}{dt} \propto E^{-\gamma} $ and experimentally $ \gamma = 2.7 \pm ? $. Consequently higher energy Cosmic Rays are heavily suppressed. The Energy Threshold for Cherenkov Light Emission as a function of height is illustrated in \ref{fig:generalenergy}. Once the Energy of a Cosmic Ray exceeds the local Cherenkov Energy Threshold of the atmosphere, the Nucleus will begin emitting a ring of Cherenkov Light.

Above threshold, Cherenkov Emission is determined by the Frank Tamm formula!!!!! A full simulation of the LPD was undertaken. Under the assumption of constant magnetic permittivity and a zenith angle of $90\degree$ we can use the approximate form \[ N_{photons} \approx (37000 \times Z^{2} \times \Delta_{h} \times \Delta_{E})\] where $\Delta_{h}$ is the vertical distance travelled in meters and $\Delta_{E}$ is the emission energy range in eV.

The Refractive Index of the atmosphere, and thus the Cherenkov angle $\theta_{C}$, increases as the altitude decreases. The refractive index at a series of heights, based on data from the HESS site, is shown \ref{fig:lpd}. Exponentials are fitted between points to provide interpolation, and a comparison can be made to a linear interpolation that is also plotted. Despite the exponential interpolation, discontinuities in the second derivative of the refractive index prevent the LPD from being smooth in the simulation. This is unimportant, because in reality the variation due to atmospheric conditions and random noise will smear out any discontinuities in the LDF.

Emission continues until the first interaction with the atmosphere, occurring at a randomly distributed height we call $h$. Then for a given Telescope Array altitude above sea level, simple trigonometry yields the radius of the LDF on the ground:
\[ Radius(height = altitude_{array}) = \tan [\theta_{C}(h)] \times (h - altitude_{array})\]

Thus the upper atmosphere emission contributes to the inner LDF, while the lower atmosphere emission contributes to the outer LDF. We can also see ground emission radius as a function of height in \ref{fig:generalenergy}. We find that the high-radius emission (occurring near the first interaction region) varies little between different high energies. We deem this to be \textquoteleft Saturated Emission\textquoteright.

To accurately quantify Saturated Emission, we can compare the photon density to the theoretical maximum photon density, corresponding to an infinite-energy particle with $\beta =1$. The illustrated maximum is useful as a reference, although because the atmosphere is not modelled beyond an altitude of 120km, the small-radius emission is not accurately simulated entirely correctly. However, real cosmic rays in the considered energy regime will all cross the emission threshold and begin emission at an altitude much lower than 120km, so can be considered accurately modelled. Absorption WAS/WAS NOT modelled.

However, in the 4 telescope height region, the Cherenkov Threshold Energy is $ E_{Threshold} \approx 0.35$ TeV per Nucleon as shown in \ref{fig:lpd}! The saturation in for these heights occurs roughly at 0.7 TeV per Nucleon or something...

@@
